AA Distributed Software Development Methodology

### 2013-06-02 paper.tex
synced w hybrid up until sec AA session
ate l 262 consolidado, agora vendo a fig aa-0_1_

\begin{figure}
\begin{center}
   \includegraphics[width=0.8\linewidth,keepaspectratio=true]{figs/aa-mm.png}
\end{center}
   \caption{
   A mindmap of our methodology
   }
\label{fig:mm}
\end{figure}

\subsection{AA session}

From the developer's perspective, the AA methodology is based on
creating pretty small high perspective reports of what they are doing
in a specific time frame, that can be something between 5 to 15
minutes, depending on what is most convenient for the developer and the team. An
\emph{AA Session} would be a period of at least 2 hours doing these periodical
\emph{micrologs} also called \emph{AA posts}. The developer can set reminders or alerts to show up when its time to
\emph{microlog}. The objective of the flexible time frame and
alert scheme is to \emph{minimize developer overhead} during his AA session. In
this way, the developer can issue micrologs while staying maximally concentrated in his
code. Each microlog may be sent directly to an on-line server, or stored
locally in a temporarily database for sending/pushing later. This enables
offline micrologging and periodical alerting.

Developers optionally record a \emph{video screencast} at the end of the
session summarizing what has been done, explaining with his words and
showing his most important results. This is very similar to the video logging system
in the movie Avatar, although it is proved from our July 2011 git repositories and online
wiki that we have used this powerful concept in AA prior to the release of
Avatar. Moreover, screencasting differs from general videologging in that it
typically captures actual workflow on
the computer screen. Screencasting, combined with the textual log of the AA
Session, renders the final report more understandable for the individual developer himself
or to other people searching for information about his production.

\subsection{AA website report}

\begin{figure}
\begin{center}
   \includegraphics[width=\linewidth]{figs/aa-0_1.png}
\end{center}
   \caption{AA Report Agregator Version 0.1}
\label{fig:aaserver}
\end{figure}

>>>>

\begin{figure}
\begin{center}
   \includegraphics[width=0.8\linewidth,keepaspectratio=true]{figs/aa-mm.png}
\end{center}
   \caption{
   A mindmap of the AA methodology: 1) `developer engagement cycle', \ie, his use
   of AA; 2) `functionality', \ie, main goals of the system; 3) `potentialities',
   \ie, enhancements AA delivers to the developer's context. 
   }
\label{fig:mm}
\end{figure}

\subsection{The AA session}

From the developer's perspective, the AA methodology is based on generating
small, high level reports called \emph{micrologs} or \emph{AA shouts} of what
they are doing in a specific period of time.  This timeframe can be
between 5 to 15 minutes in our proposed practice, depending on what is most
convenient for the developer and the team. An \emph{AA Session} is a focused
period of continuous work, lasting about 2 hours in our proposed regime, in
which the developer issues a collection of these short periodical
\emph{micrologs}. The developer can set reminders or alerts to show up when it
is time to \emph{microlog}. The objective of the flexible timeframe and alert
scheme is to \emph{minimize developer overhead} during his AA session.  In this
way, the developer can issue micrologs while staying maximally focused on
his code. Each microlog may be sent directly to an on-line server, or stored
locally in a temporarily database for sending/pushing later on.  This enables
offline micrologging and periodical alerting.

Developers optionally record a brief \emph{video screencast} at the end of the
session summarizing what has been done, explaining his goals and challenges
in his own words and showing his most important results. This is very similar to
the video logging system in the movie Avatar, although it is clear from our
July 2011 git repositories and online wiki that we have used this powerful
concept in AA prior to the release of Avatar. Moreover, screencasting differs
from general videologging in that it typically captures actual workflow on the
computer screen. Screencasting, combined with the textual log of the AA Session,
renders the final report more understandable for the individual developer
himself or to other people searching for information about his production.
% TODO: talvez figura com diagraminha explicando uma semana tipica,
% e cada sessao AA com um bloco dividido nos 15 min, e no inicio do bloco tb
% podemos listar no diagrama ``developer reads felow AA logs and lists his
% assigned tickets before he starts''

\subsection{The AA website report}

\begin{figure}
\begin{center}
   \includegraphics[width=0.95\linewidth]{figs/aa-0_1.png}
\end{center}
   \caption{AA Report Agregator Version 0.1. Messages of users hybrid, filter0,
   v1z e aut0mata about activities of interest for labMacambira.sf.net and
   related entities (IPRJ/UERJ, IFT/UNESP, IFSC/USP, OPW/Mozilla,
   PulaPirataComics). Each message is a ``shout'', which, grouped, forms an AA
   session.}
\label{fig:aaserver}
\end{figure}
